---
title: "Week 10: Result Tables"
output: html_notebook
---


# Load required libraries
```{r}

library(dplyr)
library(tidyr)

```


# Load data (Two methods)
```{r}

# Read from csv file
ESGscore_TobinsQ <- read.csv("public/ESGscore_TobinsQ_Moodle.csv")

# Load data previously saved in R native format (.RData)
load("public/ESG_data_Moodle.RData")
# Note: ESG score data from Ch.5 of https://www.greenfinance.education"

```


# Merge datasets
```{r}

ESG_data_new <- ESG_data |> 
  mutate(date = as.character(date)) |>
  left_join(ESGscore_TobinsQ, by = c("instrument" = "tic", "date" = "datadate")) |>
  mutate(
    at_pos = ifelse(at > 0, at, NA), # Replace non-positive 'at' values with NA
    ceq_pos = ifelse(ceq > 0, ceq, NA), # Replace non-positive 'ceq' values with NA
    q = (prcc_f * csho + dltt + dlc) / at_pos, # Tobin's Q calculation 
    ESGscore = esg_metric,
    Firm_Size = log(at), 
    Leverage = (dltt + dlc) / ceq_pos, 
    Year = fyear,
    Industry = sich,
    ) |> 
  select(source, q, ESGscore, Firm_Size, Leverage, Year, Industry) |>
  drop_na() # Drop any remaining rows with NA values in the selected columns

ESG_data_B <- ESG_data_new |>
  filter(source == "Provider_B") |>
  select(-source) # Remove 'source' column as it's no longer needed

ESG_data_A <- ESG_data_new |>
  filter(source == "Provider_A") |>
  select(-source)

# Keep only the merged dataset to conserve memory
rm(ESG_data_new, ESG_data, ESGscore_TobinsQ) # remove data no longer needed
gc() # Garbage collection to free up memory

```


# Summary statistics of data
```{r}

ESG_data_B |>
  summary()

```


# Descriptive statistics table
```{r}

library(modelsummary)
library(rstudioapi)

ESG_data_B |>
  select(q, ESGscore, Firm_Size, Leverage) |>
  datasummary(
    output = "default",   # or "html", "latex", "markdown", knitr::kable(), etc.
    formula = q + ESGscore + Firm_Size + Leverage ~ 
              (N = N) + (Mean = Mean) + (Median = Median) + 
              (SD = SD) + (Min = Min) + (Max = Max)
  )

```


# Correlation table
```{r}

library(correlation)

ESG_data_B |> 
  select(q, ESGscore, Firm_Size, Leverage) |>
  correlation() |> # compute correlation matrix
  datasummary_correlation(stars = TRUE)   # auto stars + note at bottom

```


# Regression analysis: Simple regression
```{r}

# Model 1: Simple regression
model1 <- lm(q ~ ESGscore, data = ESG_data_B)

summary(model1)

```


# Regression analysis: Pooled Ordinary Least Squares (OLS) without/with Year or/and industry indicators
```{r}

# Model 2: Multiple regression  
model2 <- lm(q ~ ESGscore + Firm_Size + Leverage, data = ESG_data_B)   

# Model 3: with industry fixed effects
model3 <- lm(q ~ ESGscore + Firm_Size + Leverage + factor(Industry), data = ESG_data_B)

# Model 4: industry + year fixed effects
model4 <- lm(q ~ ESGscore + Firm_Size + Leverage + factor(Industry) + factor(Year), data = ESG_data_B)

```


# Professional regression tables with side-by-side models
```{r}

library(stargazer)

suppressWarnings(  # suppress harmless warnings  
  
stargazer(
  model1, model2, model3, model4,
  
  type = "text",           # use "latex", "html", "markdown" depending on where you want to paste it
  # type = "html"   → good for R Markdown / Word
  
  title             = "MAIN RESULTS",
  dep.var.labels    = "q",               # or "Tobin's q", "Firm performance", etc.
  column.labels     = c("Model 1", "Model 2", "Model 3", "Model 4"),
  covariate.labels  = c("ESGscore", "Firm Size", "Leverage"),    
  
  # Keep only the variables you want to show (omit industry/year dummies)
  keep              = c("ESGscore", "Firm_Size", "Leverage"),
  
  # Professional style choices
  se                = list(NULL, NULL, NULL, NULL),   # default = show standard errors in ()
  star.cutoffs      = c(0.1, 0.05, 0.01),
  notes             = "Standard errors in parentheses; ***p<0.01, **p<0.05, *p<0.1",
  notes.append      = FALSE,
  
  # Custom rows for fixed effects
  add.lines = list(
    c("Industry Indicators", "No", "No", "Yes", "Yes"),
    c("Year Indicators",     "No", "No", "No",  "Yes")
  ),
  
  # Bottom statistics
  keep.stat         = c("n", "rsq"),          # show only N and R²
  digits            = 3,
  
  # Cosmetic / layout
  no.space          = TRUE,          # remove empty lines → more compact
  align             = TRUE,          # align numbers at decimal point
  font.size         = "small",       # or "footnotesize", "scriptsize", etc.
  single.row        = FALSE          # coefficients and se on separate rows (your style)
  )

)

```


# Sensitivity analysis: Alternative regression specifications or subsamples
```{r}

# Main / baseline (full sample, ESG measure + controls + fixed effects)
m_main <- model4

# Alternative ESG measure (e.g. from Provider A, instead of Provider B)
m_alt <- lm(q ~ ESGscore + Firm_Size + Leverage + factor(Industry) + factor(Year), 
             data = ESG_data_A)

# Subsample: large firms (e.g. Firm_Size above median)
m_large <- lm(q ~ ESGscore + Firm_Size + Leverage + factor(Industry) + factor(Year), 
              data = (ESG_data_B |> filter(Firm_Size > median(Firm_Size)))
              )  

# Subsample: 2010–2019
m_1019 <- lm(q ~ ESGscore + Firm_Size + Leverage + factor(Industry) + factor(Year), 
             data = (ESG_data_B |> filter(Year >= 2010 & Year <= 2019))
              )  

```


# Professional regression tables for robustness checks
```{r}

suppressWarnings(  # suppress harmless warnings  
  
stargazer(
  m_main, m_alt, m_large, m_1019,
  
  type              = "text",     # change to "html" for paper/Rmd/Word
  
  title             = "ROBUSTNESS ANALYSIS",
  dep.var.labels    = "q",  
  
  column.labels     = c("Main Results", 
                        "Alt. ESG Score", 
                        "Large Firms", 
                        "2010-2019"),
  

  # Only show ESGscore for brevity
  keep              = "^ESGscore",   
  
  # Rename coefficient(s) nicely
  covariate.labels  = "ESGscore",
  
  # Standard errors in parentheses, stars
  se                = NULL,                    # default = show in ()
  star.cutoffs      = c(0.1, 0.05, 0.01),
  notes             = "Standard errors in parentheses; ***p<0.01, **p<0.05, *p<0.1",
  notes.append      = FALSE,
  
  # Custom rows at the bottom
  add.lines = list(
    c("Controls",                  "Yes", "Yes", "Yes", "Yes"),
    c("Industry Indicators",       "Yes", "Yes", "Yes", "Yes"),
    c("Year Indicators",           "Yes", "Yes", "Yes", "Yes")
  ),
  
  # Only show N and R² at the bottom
  keep.stat         = c("n", "rsq"),
  digits            = 3,
  
  # Layout improvements 
  no.space          = TRUE,
  align             = TRUE,
  single.row        = FALSE,          # coef + se on separate rows
  font.size         = "small"         # 
  )

)

```


